Learning from Massive Noisy Labeled Data for Image Classification

### 2015-04-11 ext.tex
Polish punctuations

\title{Learning From Massive Noisy Labeled Data for Image Classification}
\addauthor{
Tong Xiao$^1$, 
Tian Xia$^2$,
Yi Yang$^2$,
Chang Huang$^2$,
and Xiaogang Wang$^1$
}{}{1}
\addinstitution{
$^1$The Chinese University of Hong Kong.
$^2$Baidu Research.
}

@@

Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively. Figure~\ref{fig:overview} shows the framework of our approach. We collect $1,000,000$ clothing images from online shopping websites. Each image is automatically assigned with a noisy label according to the keywords in its surrounding text. We manually refine $72,409$ image labels, which constitute a clean sub-dataset. All the data are then used to train CNNs, while the major challenge is to identify and correct wrong labels during the training process.

To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the true labels and uses them to supervise the training of the network. Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels. However,~\cite{sukhbaatar2014learning} assumed noisy labels are conditionally independent with input images given clean labels. By examining the collected dataset, we find that this assumption is too strong to fit real-world data well. For example, in Figure~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''. The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''. Since different sellers have their own bias on different categories, they may provide wrong keywords for similar clothes. We can capture these visual patterns to estimate how likely an image is mislabeled. Based on these observations, we further introduce two types of label noise:
\begin{itemize}
\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\emph{e.g}, the samples with ``?'' in Figure~\ref{fig:overview}).
\item \textbf{Pure random noise} makes the noisy label totally wrong. It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\emph{e.g.}, the samples with ``$\times$'' in Figure~\ref{fig:overview}).
\end{itemize}

>>>>

\title{Learning from Massive Noisy Labeled Data for Image Classification}
\addauthor{
Tong Xiao$^1$, 
Tian Xia$^2$,
Yi Yang$^2$,
Chang Huang$^2$,
and Xiaogang Wang$^1$
}{}{1}
\addinstitution{
$^1$The Chinese University of Hong Kong.
$^2$Baidu Research.
}

@@

Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively. Fig.~\ref{fig:overview} shows the framework of our approach. We collect $1,000,000$ clothing images from online shopping websites. Each image is automatically assigned with a noisy label according to the keywords in its surrounding text. We manually refine $72,409$ image labels, which constitute a clean sub-dataset. All the data are then used to train CNNs, while the major challenge is to identify and correct wrong labels during the training process.

To cope with this challenge, we extend CNNs with a novel probabilistic model, which infers the true labels and uses them to supervise the training of the network. Our work is inspired by~\cite{sukhbaatar2014learning}, which modified a CNN by inserting a linear layer on top of the softmax layer to map clean labels to noisy labels. However,~\cite{sukhbaatar2014learning} assumed noisy labels are conditionally independent with input images given clean labels. By examining the collected dataset, we find that this assumption is too strong to fit real-world data well. For example, in Fig.~\ref{fig:noise_cluster}, all the images should belong to ``Hoodie''. The top five are correct while the bottom five are either mislabeled as ``Windbreaker'' or ``Jacket''. Since different sellers have their own bias on different categories, they may provide wrong keywords for similar clothes. We can capture these visual patterns to estimate how likely an image is mislabeled. Based on these observations, we further introduce two types of label noise:
\begin{itemize}
\item \textbf{Confusing noise} makes the noisy label reasonably wrong. It usually occurs when the image content is confusing (\emph{e.g}, the samples with ``?'' in Fig.~\ref{fig:overview}).
\item \textbf{Pure random noise} makes the noisy label totally wrong. It is often caused by either the mismatch between an image and its surrounding text, or the false conversion from the text to label (\emph{e.g.}, the samples with ``$\times$'' in Fig.~\ref{fig:overview}).
\end{itemize}
